Extracting Function Signature from R Program Traces

### 2020-05-10 paper/main.tex
clean up
intro wip

\begin{document}
\title{Types for R, Empirically Designed and Evaluated}
\begin{abstract}

\end{abstract}
\maketitle

@@

@@

\AT{I can grab some of the intro Jan wrote for the last paper, rework it, and put it here.}

%
%
%
%
%
%
\section{Background}

>>>>

\begin{document}
\title{Extracting Function Signature from R Program Traces}

\begin{abstract}
  This paper documents the first steps towards retrofitting a type system
  onto the R programming language. We introduce an extension of R with
  function signatures. To evaluate the fit of our design to the language, we
  start by automatically extracting the signatures for 500 widely used
  packages. In a second step we use the reverse dependencies of these
  packages to validate that these signatures are accurate.
\end{abstract}
\maketitle

@@

How does one retrofit a type system to an existing language? Three succesful
models are Hack, Typed Racket and TypeScript.

@@

%
%
%
\section{Background}
